Untitled

### 2017-02-15 Code/calculate_std_mort_rates.Rmd

system.time(
  for(i in 1:8){
    print(i)
    load(paste0("~/BW_results/results_set_", i, ".Rdata"))
    r.All <- merge(r.All, std.pop, by = "age_minbin")

@@

    mortality.rates.summary <- add_Census_Division(mortality.rates.summary, state)
    mortality.rates.summary <- add_Census_Region(mortality.rates.summary, state)
    mortality.rates.summary$stabbrs <- state.abb[match(mortality.rates.summary$state, state.name)]
    mortality.rates.summary$rate.per.100k <- mortality.rates.summary$age.std.mortality.rate_med*100000
    mortality.rates.summary <- mortality.rates.summary %>% mutate(state.reorder = reorder(state, as.numeric(Census_Division)))

@@

    mortality.rates.difference %>% mutate(state.reorder = reorder(state, as.numeric(Census_Division)))

>>>>

system.time(
  for(i in 2:8){
    print(i)
    load(paste0("~/BW_results/results_set_", i, ".Rdata"))
    r.All <- merge(r.All, std.pop, by = "age_minbin")

@@

    mortality.rates.summary <- add_Census_Division(mortality.rates.summary, state)
    mortality.rates.summary <- add_Census_Region(mortality.rates.summary, state)
    mortality.rates.summary$stabbrs <- state.abb[match(mortality.rates.summary$state, state.name)]
    mortality.rates.summary$rate.per.100k <- mortality.rates.summary$age.std.mortality.rate_med*100000
    mortality.rates.summary <- mortality.rates.summary %>% mutate(state.reorder = reorder(state, as.numeric(Census_Division)),
                                                                  age.std.mortality.rate_LCL = age.std.mortality.rate_LCL*100000,
                                                                  age.std.mortality.rate_med = age.std.mortality.rate_med*100000,
                                                                  age.std.mortality.rate_UCL = age.std.mortality.rate_UCL*100000)

@@

    #tidy mortality rates summary
    mortality.rates.difference$COD <- factor(mortality.rates.difference$COD, COD.levels)
    mortality.rates.difference <- add_Census_Division(mortality.rates.difference, state)
    mortality.rates.difference <- add_Census_Region(mortality.rates.difference, state)
    mortality.rates.difference$stabbrs <- state.abb[match(mortality.rates.difference$state, state.name)]
    mortality.rates.difference <- mortality.rates.difference %>% mutate(state.reorder = reorder(state, as.numeric(Census_Division)),
                                                                        rate.difference_LCL = rate.difference_LCL*100000,
                                                                        rate.difference_med = rate.difference_med*100000,
                                                                        rate.difference_UCL = rate.difference_UCL*100000)
